Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-07-21 manuscript/supplement_motifs.tex

    \begin{figure}[h!]
        \centering
        \includegraphics[width=.95\textwidth]{figures/roles_vs_SC.eps}

        \caption{The proportion of each motif in a species' participation vector varied with network size, connectance, and their interaction. These relationships were steepest for apparent competition and omnivory.}
        \label{fig:roles_vs_SC}
    \end{figure}
\clearpage

@@

    \subsection*{}

>>>>

    \begin{figure}[h!]
        \centering
        \includegraphics[width=.95\textwidth]{figures/participation_vs_SC.eps}
        \caption{The proportion of each motif in a consumer's participation vector varied with network size, connectance, and their interaction. These relationships were steepest for apparent competition and omnivory.}
        \label{fig:roles_vs_SC}
    \end{figure}
\clearpage

@@

    \subsection*{Motif participation and proportion of basal resources}

        We fit regressions relating the proportion of each motif in a consumer's motif participation vector to the proportion of basal resources in the network (pBasal), connectance, and the interaction between them.
        Participation in all four motifs was significantly related to pBasal, connectance, and the interaction between them (Fig.~\ref{fig:basal_participation}).

        \begin{figure}
            \centering
            \includegraphics{}
            \caption{Caption}
            \label{fig:basal_participation}
        \end{figure}

        Participation in the three-species chain increased in networks with more basal resources ($\beta_{pBasal}$=0.0447, $p$\textless0.001), decreased in more-connected networks ($\beta_C$=-0.296, $p$\textless0.001), and decreased with the interaction between them ($\beta_{pBasal:C}$=-0.525, $p$\textless0.001).
        Participation in the omnivory motif decreased in networks with more basal resources ($\beta_{pBasal}$=-0.198, $p$\textless0.001), increased in more-connected networks ($\beta_C$=0.701, $p$\textless0.001), and increased strongly with the interaction between them ($\beta_{pBasal:C}$=2.81, $p$\textless0.001).
        Participation in the apparent competition motif decreased in networks with more basal resources and more-connected networks ($\beta_{pBasal}$=-0.0825, $p$\textless0.001 and $\beta_C$=-0.846, $p$\textless0.001) but increased strongly with the interaction between them ($\beta_{pBasal:C}$=1.66, $p$\textless0.001).
        Participation in the direct competition motif increased in networks with more basal resources and more-connected networks ($\beta_{pBasal}$=0.235, $p$\textless0.001 and $\beta_C$=0.442, $p$\textless0.002), but decreased strongly with the interaction between them ($\beta_{pBasal:C}$=-3.94, $p$\textless0.001).
